Everest Bio

### 2022-02-13 xar-EB-general/index.Rmd
presentation

---
title: "Everest Bio"
subtitle: |
  **ÉV**aluation du r**É**seau de **RE**cyclage pour **S**outenir la **T**ransition vers une **BIO**économie <br/>
  Projet de recherche CREIDD et ERPI
author: "Fabio Cruz / Mauricio Camargo / Nadège Troussier"
institute: "CREIDD, ERPI"
date: '2020/11/18 (updated: `r Sys.Date()`)'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["default"]
    seal: false 
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      beforeInit: "assets/macros.js"
      navigation:
        scroll: false # disable slide transitions by scrolling
---

```{r setup, include = FALSE, echo=FALSE, message=FALSE}
options(htmltools.dir.version = FALSE)

knitr::opts_chunk$set(include= TRUE, echo=FALSE, message=FALSE, fig.path="figures/")

library(readxl)
library(here)
library(flextable)
library(tidyverse)

@@

```{r, include=TRUE, echo=FALSE}
# CSS for the CSS
htmltools::includeCSS("https://raw.githubusercontent.com/fabbiocrux/presentaciones/gh-pages/Assets-global/css/Fabio-fonts.css")
htmltools::includeCSS("https://raw.githubusercontent.com/fabbiocrux/presentaciones/gh-pages/Assets-global/css/Fabio.css")
```

```{r share-again, echo=FALSE}
xaringanExtra::use_share_again()
```

@@

# `r rmarkdown::metadata$title`

@@

### `r rmarkdown::metadata$date`

@@

```{r, include=FALSE}
Fabio <- TRUE
```

```{r, child= if (!Fabio) 'partials/Fabio-presentation.Rmd'}

```

.pull-left[
1. .content-box-yellow[ERPI Laboratory]
1. Green Fablab
1. Everest Bio
1. Proposition and Research axis
]

.brand-blue[Equipe de Recherche sur le Processus Innovatifs - ERPI]

```{r, out.width = '80%', fig.align='center'}
knitr::include_graphics('https://erpi.univ-lorraine.fr/assets/images/logo-ERPI.svg')
```
]

## .small[Equipe de Recherche sur le Processus Innovatifs - ERPI]

A .red[Multidisciplinary] team in **Industrial Engineering** specialized in the study of Innovation processes

```{r, out.width = '95%', fig.align='center'}
knitr::include_graphics('https://erpi.univ-lorraine.fr/assets/images/logo-ERPI.svg')
```

45 Members average

24 permanent researchers <br>
(10 full Pr., 13 associated Pr, 1 Research engineer) <br>
1 Studies engineer <br>
5 Postdoc  <br>
3 Temporary lecturers  <br>
2 Admin. <br>

```{r, out.width = '95%', fig.align='center'}
knitr::include_graphics(paste0(URL, 'LF2L/Methodology-complet-00.jpg'))
```

Research platform: **LF2L** - http://lf2l.fr
]

# Research domains at ERPI:

.pull-left[
.pull-left[
```{r, out.width = '95%', fig.align='center'}
knitr::include_graphics(paste0(URL, 'ERPI/Presentation/01-Innovation-metrology.jpg'))
```

.orange[
**Innovation capability**

Product <br>
Process  <br>
Business Model <br>

]
]
.pull-right[
```{r, out.width = '95%', fig.align='center'}
knitr::include_graphics(paste0(URL, 'ERPI/Presentation/02-Prospective.jpg'))
```
.blue[
**Technological  Emergence/maturity**

Product-Process <br>
Industrial supply chain <br>
]]]

.pull-right[
.pull-left[
```{r, out.width = '95%', fig.align='center'}
knitr::include_graphics(paste0(URL, 'ERPI/Presentation/03-Design.jpg'))
```
.green[
**Materialized**

Creative Exploration <br>
Feasibility Product-Process <br>
Physic & digital (virtual) Prototyping <br>
]
]
.pull-right[
```{r, out.width = '95%', fig.align='center'}
knitr::include_graphics(paste0(URL, 'ERPI/Presentation/04-Acceptability.jpg'))
```
.purple[
**Front-end validation**
Multi-actors Acceptability <br>
User eXperience & test by use <br>
Living Lab <br>
]]]

.center.Large[Creator of **methods & tools** supporting innovation process]

## Scope: The Fuzzy Front End of innovation

.pull-left[
```{r, out.width = '95%', fig.align='center'}
knitr::include_graphics(paste0(URL, 'ERPI/Presentation/Scope-00.jpg'))
```
]

.pull-right[
```{r, out.width = '95%', fig.align='center'}
knitr::include_graphics(paste0(URL, 'ERPI/Presentation/Purpose-00.jpg'))
```
.footnote[
Martinez-Hernandez, E., 2017. Trends in sustainable process design—from molecular to global scales. Curr. Opin. Chem. Eng. 17, 35–41. <br/> https://doi.org/10.1016/j.coche.2017.05.005 
]
]

Think earlier in the sustainable design and their impact

## Innovation: a response to current social challenges

```{r, out.width = '95%', fig.align='center'}
knitr::include_graphics(paste0(URL, 'ERPI/Presentation/Fields-00.jpg'))
```

.tiny[Tran Thi Hoang, G., Dupont, L., & Camargo, M. (2019). Application of Decision-Making Methods in Smart City Projects: A Systematic Literature Review. Smart Cities, 2(3), 433-452.]

@@

class: top, left
background-image: url(`r paste0(URL, 'Plastics/Plastic-problem-03.svg')`)
background-position: right
background-size: 70%

## Plastics waste since  olden times

.left-column[
.tiny[
- US recycled less than 9% of its plastic waste.
- EU, recycled about 30%. However, this number is what is collected, not from what is in circulation*. 
- China’s ban on plastic trash
- Plastic trash could top 13 billion tons by 2050
- Economics of plastic recycling historically have been challenging
- Little financial incentive to encourage consumers to recycle their own plastic waste

```{r, out.width = '60%', fig.align='center'}
knitr::include_graphics('https://images.unsplash.com/photo-1537084642907-629340c7e59c?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1567&q=80')
```

]]

.footnote[
Geyer, R., Jambeck, J.R., Law, K.L., 2017. Production, use, and fate of all plastics ever made. Sci. Adv. 3, e1700782. https://doi.org/10.1126/sciadv.1700782

*Kranzinger, L., Pomberger, R., Schwabl, D., Flachberger, H., Bauer, M., Lehner, M., Hofer, W., 2018. Output-oriented analysis of the wet mechanical processing of polyolefin-rich waste for feedstock recycling. Waste Manag. Res. 36, 445–453

@@

.left-column[
.footnotesize[
- Only technico-economic criteria alone do not (no longer) enables a informed decision making 
- Need to assess value chains in a different way, including actual impacts on ecosystems
- A more holistic vision is needed to assess the feasibility of these new sectors.
]
 ]

.right-column[ 
.polaroid[ ![](figures/Recycling.png) ]
]

@@

## Green Fablab: Towards a distributed recycling via additive manufacturing (DRAM)

@@

@@

```{r, include=TRUE, echo=FALSE, out.width = '100%', fig.align='center'}
knitr::include_graphics(paste0(URL, 'Green-Fablab/Green-fablab-1.jpg'))
```

@@

## Green Fablab: Towards a distributed recycling via additive manufacturing (DRAM)

@@

@@

## People in Everest Bio

@@

## Purpose of Everest Bio

@@

# Delivrables & Valorisations

>>>>

---
title: "Everest Bio"
subtitle: |
  **ÉV**aluation du r**É**seau de **RE**cyclage pour **S**outenir la **T**ransition vers une **BIO**économie <br/>
author: "Fabio Cruz / Mauricio Camargo / Nadège Troussier"
institute: "CREIDD, ERPI"
#date: "2020/11/18 (updated: Sys.Date())"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["assets/xaringan-themer.css", "assets/EB.css"]
    seal: false 
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      beforeInit: "assets/macros.js"
      navigation:
        scroll: false # disable slide transitions by scrolling
---

```{r setup, include = FALSE, echo=FALSE, message=FALSE}
options(htmltools.dir.version = FALSE)
source("xaringan-themer.R")

library(vembedr)

knitr::opts_chunk$set(
   include = TRUE,
  fig.width=9, fig.height=3.5, fig.retina=3,
  fig.path="figures/",
  out.width = "100%",
  fig.align = 'center',
  cache = FALSE,
  echo = FALSE,
  message = FALSE, 
  warning = FALSE,
  fig.show = TRUE,
  hiline = TRUE
)

@@

@@

<br>
# `r rmarkdown::metadata$title`

@@

###**L'ingénierie et le management de l'innovation au service de la transformation des territoires**

### `r Sys.Date()`

@@

exclude: true
class: middle

@@

class: middle, left
background-image: url(`r paste0(URL, 'Plastics/Plastic-problem-03.svg')`)
background-position: 100% 20%
background-size: 70%

.left[
## Plastics waste
]

.footnote[
- Geyer, R., Jambeck, J.R., Law, K.L., 2017. Production, use, and fate of all plastics ever made. Sci. Adv. 3, e1700782. https://doi.org/10.1126/sciadv.1700782

<!-- - Kranzinger, L., Pomberger, R., Schwabl, D., Flachberger, H., Bauer, M., Lehner, M., Hofer, W., 2018. Output-oriented analysis of the wet mechanical processing of polyolefin-rich waste for feedstock recycling. Waste Manag. Res. 36, 445–453 -->

@@

class: bg-gf middle

# Green Fablab: 
## .bg-green[ a demostrotar of: <br>*'design global, manufacturing [recycling] local'*]

@@

# Green Fablab:

@@

```{r, include=TRUE, echo=FALSE, fig.cap=" ", out.width = '100%', fig.align='left'}
knitr::include_graphics(paste0(URL, 'Inedit/INEDIT-logo-00.jpg'))
```

.pull-right[
```{r}
embed_youtube(
  "sJfIU2uE7Zs",
  width = 400,
  height = 500,
  ratio = "4by3",
  frameborder = 0,
  allowfullscreen = TRUE,
)
```
]

# Green Fablab:

@@

@@

## Green Fablab

@@

exclude: true

@@

---
background-image: url(`r paste0(URL, 'Recycling/Polymer-recycling-02.png')`)
background-position: 50% 100%
background-size: 60%

- Only **.red[tech-economic criteria]** alone do not (no longer) enables a .orange[informed decision making]. 
- Need to assess value chains in a different way, including **actual impacts on ecosystems**
- A more holistic vision is needed to assess the feasibility of these new bottom-up sectors for **territorial and industrial agents**.

@@

## Purpose of the project

@@

exclude: true
## People in Everest Bio

]
---
# Delivrables & Valorisations
